R Python, and Ruby clients for GBIF species occurrence data

### 2017-09-06 use-cases/city-diversity.Rmd
added Ruby client and fixes use case problems, updated circleci badge in readme

```{r include=FALSE}
opts_chunk$set(
  warning = FALSE,
  message = FALSE,
  comment = '#>',
  collapse = TRUE,
  fig.width=8,
  fig.height=6,
  cache.path = "cache/"
)
```

@@

```{r load}
library("rgbif")
library("ggplot2")
library("plyr")
library("httr")
library("RColorBrewer")
```

@@

```{r newsearch}
getdata <- function(x){
  coords <- as.numeric(x[c('minlon','minlat','maxlon','maxlat')])
  num <- occ_search(geometry = coords, limit = 1)$meta$count
  data.frame(
    city = x['city'], 
    richness = num, 
    stringsAsFactors = FALSE
  )
}
```

>>>>

```{r include=FALSE}
opts_chunk$set(
  warning = FALSE,
  message = FALSE,
  comment = '#>',
  collapse = TRUE,
  fig.width = 8,
  fig.height = 6,
  cache.path = "cache/"
)
```

@@

```{r load}
library("rgbif")
library("ggplot2")
library("plyr")
library("httr")
library("RColorBrewer")
library("wicket")
```

@@

```{r newsearch}
getdata <- function(x){
  coords <- as.numeric(x[c('minlon','minlat','maxlon','maxlat')])
  wkt <- wicket::wkt_correct(wicket::bounding_wkt(values = coords))
  num <- occ_search(geometry = wkt, limit = 1)$meta$count
  data.frame(
    city = x['city'], 
    richness = num, 
    stringsAsFactors = FALSE
  )
}
```

### 2017-09-06 use-cases/oak-occurrences.Rmd
added Ruby client and fixes use case problems, updated circleci badge in readme

```{r}
library('rgbif')
library('raster')
library('sp')
library('maptools')
library('rgeos')
library('scales')
```

@@

```{r cache = TRUE}
url <- 'http://esp.cr.usgs.gov/data/little/querloba.zip'
tmp <- tempdir()
download.file(url, destfile = "~/querloba.zip")
unzip("~/querloba.zip", exdir = tmp)
ql <- readShapePoly(file.path(tmp, "querloba.shp"))
```

>>>>

```{r}
library('rgbif')
library('raster')
library('sp')
library('sf')
library('rgeos')
library('scales')
```

@@

```{r cache = TRUE}
url <- 'https://github.com/sckott/gbifms/blob/gh-pages/querloba.zip?raw=true'
tmp <- tempdir()
download.file(url, destfile = "querloba.zip")
unzip("querloba.zip", exdir = tmp)
ql <- sf::read_sf(file.path(tmp, "querloba/querloba.shp"))
```
